% MSc thesis style for TU Delft Embedded Networked Systems Group.

% MIT License
%
% Copyright (c) 2023 TU Delft Embedded Systems Group and Casper Dennis van Wezel.
%
% Permission is hereby granted, free of charge, to any person obtaining a copy
% of this software and associated documentation files (the "Software"), to deal
% in the Software without restriction, including without limitation the rights
% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
% copies of the Software, and to permit persons to whom the Software is
% furnished to do so, subject to the following conditions:
%
% The above copyright notice and this permission notice shall be included in all
% copies or substantial portions of the Software.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
% SOFTWARE.

\documentclass[10pt,twoside,a4paper]{report}

% add new packages here

% math packages
\usepackage{amsmath}
\usepackage{amssymb}

% textblocks for title page
\usepackage[absolute]{textpos}

% use babel for proper hyphenation
\usepackage[british]{babel}

% Graphics: different for pdflatex or dvi output, choose one
%%\usepackage[dvips]{graphicx}
%%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}

\usepackage{epstopdf}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{placeins} % provides \FloatBarrier to keep figures near their text

% Make captions distinguishable
\usepackage[textfont=bf]{caption}

% Chose font style
\usepackage[scaled=.92]{helvet}

% for url's use "\url{http://www.google.com/}"
\usepackage{url}
\usepackage[plainpages=false]{hyperref}

% Placeholder boxes for figures still to be produced (\missingfigure)
\usepackage{todonotes}

% TikZ for the controller block diagram and the navigation state machine
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, calc, angles, quotes}

% Information that will be filled in at various points in the report
\newcommand{\reportTitle}{Drawn to the Light: Autonomous Optical Navigation for Micro-Drones}
\newcommand{\reportAuthor}{Bart van Maris} % Please put your full and official name here: no abbreviations (and to Dutch students: geen roepnamen)
\newcommand{\studentNumber}{5108748}
\newcommand{\reportEmailTUD}{b.j.vanmaris@student.tudelft.nl}
\newcommand{\reportEmailNonTUD}{bartvanmaris@hotmail.nl}
\newcommand{\reportUrlEmailTUD}{\href{mailto:\reportEmailTUD}{\reportEmailTUD}}
\newcommand{\reportUrlEmailNonTUD}{\href{mailto:\reportEmailNonTUD}{\reportEmailNonTUD}}
\newcommand{\reportMSC}{Computer and Embedded Systems Engineering} % Examples are {Embedded Systems} {Computer Engineering} {Computer Science} or {Electrical Engineering}
\newcommand{\reportDate}{PUT DATE OF PROVIDING THESIS TO GRADUATION COMMITTEE HERE}
\newcommand{\presentationDate}{9th of July}
\newcommand{\graduationCommittee}{
Marco Zuñiga Zamalloa & Delft University of Technology \\
Gosia Migut & Delft University of Technology \\
Harry Huang & Delft University of Technology \\
}

% Provide full name and surname (no abbreviations), so "Koen Langendoen" not "K. Langendoen"

% The order of listing above: 

% title + Graduation committee chairman name and surname (chairman)
% title + Supervisor 1 name and surname (direct supervisor)
% title + Supervisor 2 name and surname (direct supervisor)
% ...
% title + Supervisor X name and surname (direct supervisor) 
% ...
% Others (ordered by title and alphabetical)

% Example: 
% prof.\,dr.\,Koen Langendoen (chairman) & Delft University of Technology \\ 
% dr.\,Przemys{\l}aw Pawe{\l}czak & Delft University of Technology \\ 

\newcommand{\reportAbstract}{Small drones increasingly operate indoors, where GPS is unavailable and the heavier sensors normally used for indoor positioning exceed a micro-drone's weight, size, and power budget. Visible light is a practical alternative, because the spaces a drone operates in are already lit. An ordinary lamp can be modulated to act as a navigation beacon, while the drone carries only a small light sensor to detect it. Prior work by Huang et al.\ navigates a micro-drone toward a single such beacon, recovering the direction of the light from a ring of photodiodes. That work was demonstrated only in simulation, and it keeps no record of the light field. It therefore cannot distinguish one beacon from another, nor route around an obstacle that blocks the light.

This thesis gives a weight-, size-, and power-constrained micro-drone the navigation those methods lacked, using only on-board light sensing. We design a fused controller that combines two directions. The first is the bearing toward the beacon, read from a ring of photodiodes. The second is a gradient, which the drone estimates from a map of the light field that it builds as it flies. Because the map is built from all eight photodiodes, the gradient no longer depends on the drone's heading, as it did in the prior single-photodiode method. The sensing runs on a custom photodiode board of about 6~grams and 42~millimetres, within the payload budget of a CrazyFlie~2.1. A signal pipeline on the drone then recovers each beacon from the board's noisy output through a frequency analysis, and reports a confidence measure for each reading. We validate the approach in a Webots simulation and in real flight. The drone reaches several modulated beacons in turn, and routes around an obstacle, using its stored map of the light field when the obstacle blocks the beacon. In a later collaboration, Huang et al.\ flew the same board and controller on a lighter-than-air blimp, which shows that the approach generalises across platforms.}

\newcommand{\reportKeywords}{visible light communication; light-seeking navigation; GPS-denied indoor navigation; micro-drone; multi-target navigation; obstacle avoidance; bearing angle estimation; gradient-based source seeking; photodiode array}

% Did the thesis lead to a paper? 
% e.g. The work presented in this thesis has lead to a paper which has been submitted to a conference for publication, pending peer-review
%\newcommand{\reportPaper}{LINE ABOUT YOUR PUBLICATION GOES HERE}
\newcommand{\reportPaper}{}


% Information for pdflatex
\pdfinfo{
/Author (\reportAuthor)
/Title (\reportTitle)
/Keywords (\reportKeywords)
}

\begin{document}

\pagenumbering{alph}
\pagestyle{empty}

% Make frontcover
\input{template/frontcover}

% Set marginns
\hoffset=1.63cm
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=5in

%
\parindent=1em

% Empty page
\cleardoublepage

\pagestyle{plain}
\pagenumbering{roman}
\setcounter{page}{1}

% Create title page: page i (hidden)
\input{template/titlepage}

% Create Graduation Data and Abstract: pages ii and iii (hidden)
\input{template/graduationdata}

% Empty page: page iv
\cleardoublepage

% Create preface: page v
\input{chapters/preface}

% Empty page: page vi
\cleardoublepage

% Create tabe of contents: page vii
\tableofcontents

\cleardoublepage

\pagenumbering{arabic}
\setcounter{page}{1}

% Create Introduction: page 1
\include{introduction}

% Create chapters
\input{chapters/chapter_1}
\input{chapters/chapter_2}
\input{chapters/chapter_3}
\input{chapters/chapter_4}
\input{chapters/chapter_5}
\input{chapters/chapter_6}

% Create conclusions
\input{chapters/conclusions}

% Create future work
\input{chapters/futurework}

% Create bibliography
\bibliographystyle{plain} % Please do not change the style of bibliography (yes, it should be `plain`)
\bibliography{../bib/MyMScTUDESThesisBibFile} % remove "../" before "bib" if you compile directly in Overleaf or in your favourite local LaTeX distribution

% Create appendix
\appendix
\input{chapters/appendix_a}

\end{document}
