\chapter{PCB Hardware Design}
\label{chp:hardware}

\section{Design Requirements}

The photodiode board was designed to meet two hard constraints: a total mass below 13 grams and a maximum diagonal 
footprint of 44\,mm, imposed by the CrazyFlie~2.1 platform's payload and form factor limits.

\hlnotein{\section{Circuit Design}}{one thing to think about here, previously is good to mentioned we 
need to design a board below 13g. we can mentioned before people usually use opt101(what weight and 
its too heavy and bulky.) here for each module, we need to say why we need it? for example, the 
trasimpedance amplifier help us to increase the phodiode's voltage and help us to tune the response etc.}

Eight photodiodes are arranged in a ring and each connected to a transimpedance amplifier 
that converts the photodiode's current output to a measurable voltage signal.

The voltage outputs are digitised by an ADC module that communicates with the CrazyFlie's
onboard processor over SPI, providing all eight channel readings at each sample.

The board includes optional first-order filter pads at each channel, allowing a low-pass
or high-pass filter to be populated depending on the noise characteristics of the deployment environment.

\hlnote{\section{PCB Layout}}{try to talk about why the layout and number choice. I have some previous
result, let's ask marco whether we can use it here. the teensy one pop out here. that's why we should mentioned the
old prototype before and its limitation.}

The eight photodiodes are uniformly distributed at 45\textdegree{} intervals around the full 360\textdegree{} circumference of the board to provide symmetric angular coverage.

A ground plane is included in the PCB layout to reduce the impact of electromagnetic interference generated by the drone's motors on the photodiode signal readings.

Before integration with the drone, the assembled board was verified to produce correct voltage readings on all eight channels using a standalone Teensy microcontroller.
