\chapter{Problem \& Algorithm Design}
\label{chp:algorithm}

\section{Why Existing Methods Fall Short}

A bearing-only controller drives the drone straight toward the light, which works in open space but fails as soon as an obstacle blocks the line of sight, since the drone has no memory of the light field and cannot route around the obstruction.

Following the light gradient with a single photodiode is slow and noisy, and on its own it does not give a reliable heading toward the source.

Neither approach handles more than one beacon, because nothing in them distinguishes or sequences multiple light sources.

We demonstrate these shortcomings in simulation, and the remainder of this chapter develops a controller that overcomes them; the supporting results are presented in Chapter~\ref{chp:obstacle}.

\section{System Overview}

The navigation controller fuses a bearing angle signal and a gradient ascent signal through a state machine that selects the appropriate navigation mode based on signal strength and map coverage.

% TODO: Figure --- block diagram showing state machine, map, bearing input, gradient input, and heading output

\section{Bearing Angle}

The controller's first input is a bearing angle, computed from the differential magnitudes across the photodiode ring by the prior bearing algorithm of Harry Huang~\cite{}.

The bearing is only trusted when its signal strength exceeds a minimum threshold, so that a weak or absent signal does not produce a spurious heading.

To navigate between several beacons, each is modulated at a distinct frequency so the controller can track one at a time, and the switch between frequencies was developed with simple Teensy experiments and requires that the frequencies avoid harmonic relationships.

\section{Light Intensity Map}

As the drone flies, it accumulates a spatial map by storing the strongest measured light signal at each visited location, which increases as the drone approaches the light source.

\section{Gradient Estimation}

The controller estimates the light gradient from all eight photodiodes rather than the single photodiode used in prior work, giving a faster and more stable direction of steepest increase.

Five candidate methods for estimating the gradient from the map are considered, from plane fits to a curved surface fit, and their accuracy is compared in this chapter to select the one the controller uses.

% TODO: gradient method comparison (dense probe map, sparse coverage) --- relocated from the old Simulation Experiments chapter

\section{Controller State Machine}

The state machine sequences the drone through searching, aligning, approaching, dwelling, and recovering phases for each beacon in a multi-target mission.

The recovering phase lets the drone keep moving on the gradient alone when the bearing is lost but the map is still reliable, allowing it to continue past an obstacle that blocks the direct signal.

\section{Control Output}

The controller merges the bearing and gradient directions into a single target heading and sets a forward speed, which are passed to the drone's flight controller.
