\chapter{Conclusions}
\label{chp:conclusions}

In this thesis, we ask a central question for autonomous drone deployment: how can autonomous navigation be provided on a weight-, size-, and power-constrained micro-drone with minimal changes to the environment? We address this question with a visible-light navigation system that uses a lightweight onboard light sensing system to guide the drone toward modulated light beacons, requiring only minimal modification to existing lighting infrastructure. To make our system more robust in cluttered indoor environment and real application, we develop a complete system that enables the drone to visit multiple targets in sequence and avoid obstacles that partially block the direct path to the light source.

The work builds on the light-guided navigation system proposed by Huang et al.~\cite{huang2026lta}, especially their bearing-angle estimation and gradient-based light-source seeking algorithms. The bearing estimate provides an immediate direction toward a visible beacon, but it keeps no memory of the space the drone has already observed. The gradient method, in contrast, can follow changes in the light field, but it is slower because it must infer direction from measurements gathered during motion. These methods are insufficient for the more realistic missions considered in this thesis. They do not by themselves provide robust sequencing across multiple beacons, and a bearing-only controller can still fail when an obstacle weakens or blocks the direct light signal, even though it is reported as the most efficient method in open-space source seeking.

This thesis closes these gaps under the constraints of a micro-drone. It introduces a lightweight photodiode sensing board, a frequency-domain signal pipeline for separating modulated beacons, and a fused controller that combines bearing guidance with a light-field map. Together, these components allow the drone to use the bearing estimation when the beacon is visible, fall back on the stored gradient when the direct signal becomes unreliable, and switch between beacons during longer missions. The rest of this chapter revisits how each part contributes to this result and discusses the current limitations that bound the system’s performance and motivate future improvement.

Chapter~\ref{chp:algorithm} develops the controller at the centre of the thesis. It is a fused controller that combines the bearing with a gradient estimated from a light map the drone builds as it flies. The light map, described in Section~\ref{sec:light-intensity-map}, records the light field across the area the drone has flown: as the drone moves, it writes the strongest reading of its photodiode array into a grid cell indexed by its position. Because the map is built from the full eight-photodiode array, it records a usable value at each visited location whichever way the drone faces. This removes the dependence on heading and motion that limits the single-photodiode method. The controller then estimates the gradient from this map by fitting a plane to the cells around the drone, as Section~\ref{sec:gradient-estimation} sets out. We select weighted least squares for this fit, after comparing five candidate estimators on the same field in Section~\ref{sec:gradient-estimator-comparison}. It returns a usable direction across almost the whole map, at a low and constant computational cost the microcontroller can afford. Finally, the state machine of Section~\ref{sec:state-machine} sequences a mission and decides, at each moment, whether to steer on the bearing, on the bearing and gradient blended together, or on the gradient alone. \textcolor{red}{This is too much like a recap. this chapter is not for recapping the detail. it is for what is the most important thing you want the reader to get. if you want to mentioned again these method, what is the most important stuff for people to take away?}

The first research question asks whether such a drone can carry the light sensing it needs on board and recover a reliable beacon signal in flight. Two parts of the thesis answer it together. \textcolor{red}{please split the question into two sencond. the first, the second. and it needs to provide what is important solution from this thesis, otherwise it is more like introduction.}

Firstly, Chapter~\ref{chp:hardware} presents the sensing board. It replaces an earlier Teensy prototype, described in Section~\ref{sec:original-prototype}. That prototype, at about 44~grams and 90~millimetres across, was far too large and heavy for the CrazyFlie. The new board fits eight surface-mount photodiodes and their amplifiers into about 6~grams and 42~millimetres. This is within the 13~gram and 44~millimetre limit that Section~\ref{sec:platform} derives from the platform. Section~\ref{sec:design-requirements} records that the finished board meets the set requirements. The new board carries no processor of its own and offloads all computation to the CrazyFlie. It therefore spends neither mass nor power on hardware the CrazyFlie already provides. \textcolor{red}{again too much detail tha make this redundant. for example 44 grams to the comparison to the drone size and the mentioning of the prototype size is really not necessary.}

Secondly, Chapter~\ref{chp:realworld} recovers the beacon from the board's raw output. Each photodiode reports a single voltage in which the beacon is buried under ambient light, electrical interference, and vibration. The pipeline of Section~\ref{sec:intensity-to-snr} takes a Fourier transform of each channel and reads the height of the peak at the beacon's modulation frequency as the recovered signal. It then divides that peak by the noise floor of the spectrum to report a signal-to-noise ratio, which states how far the reading can be trusted, as that section illustrates. Building the pipeline up one stage at a time shows what makes it work: estimating the noise floor with a median, so the occasional interference spike does not inflate it. As Section~\ref{sec:filter-validation} reports, the median floor more than doubles the in-flight ratio, from about 15 to about 32. The hardware anti-alias filter complements it by keeping the floor low, an effect that section also isolates. Together the board and the pipeline let a constrained micro-drone carry its light sensing on board and return a reliable beacon signal in flight, which answers the first research question. \textcolor{red}{Please shrink this and the previous paragraph. and no need to mention again the noise source etc. and the divides the peak ito get the SNR is also not necessary. for me there is only one thing important. the median floor method double ratio and what different filter matters}

The second research question asks whether the drone can then navigate to several distinct beacons in turn. \textcolor{red}{I modify the start of this section. However, for me it feel likes again its not well structure even in the original writing. it out of no where come up with a lot of research question. the thing you should do is mentioned there is two goal we want to do and there is four challenge we need to solve and then explain them in slightly detail} Chapter~\ref{chp:multibeacon} answers it in two stages. Each beacon is modulated at its own frequency. A single frequency analysis of one recording therefore holds a separate peak for each beacon. The controller selects a target by reading the peak at its frequency. On the static bench of Section~\ref{sec:multibeacon-setup}, the experiment of Section~\ref{sec:freq-separation} confirms that two beacons are recovered cleanly and at the same time, each one rising to a clear peak at its own beacon. That experiment maps the two recovered fields and shows that the signal-to-noise ratio gives a far cleaner field than the raw magnitude. Dividing by the noise floor normalises away both the per-sensor gain differences and the broadband interference. The full system then flies the CrazyFlie to two beacons in turn, as Section~\ref{sec:multibeacon-traverse} shows. The state machine of Section~\ref{sec:state-machine} runs its phases once per beacon and advances on arrival. This shows that a constrained micro-drone can navigate to several distinct light beacons in turn using only on-board light sensing, which answers the second research question. \textcolor{red}{This paragraph should be also able to shrink at least into half. a lot of detail should be exclude. for example, chapter answers it in two stages. its no need to give how specifically we solve this. }

The third research question asks whether the drone can navigate around an obstacle that blocks its line of sight to a beacon. Chapter~\ref{chp:obstacle} answers it first in simulation and then in flight. In the simulated scene where both baselines fail, the bearing-only controller collides with the pillar and the single-photodiode gradient stalls against it, as Section~\ref{sec:existing-methods-fall-short} shows. The fused controller instead blends the gradient into its heading and curves cleanly around the pillar to the beacon, which Section~\ref{sec:obstacle-sim} reports. The avoidance comes from the fusion itself, not from any fallback. On the real drone, two flights show the controller drawing on the map only as far as each situation needs. In the first flight, reported in Section~\ref{sec:obstacle-realflight}, the drone passes through enough of the obstacle's shadow that the beacon signal drops below the bearing's trust threshold. The state machine then enters its recovering phase, following the gradient from the stored map alone until the beacon returns. In the second flight, reported in the same section, the drone skirts the edge of the shadow and keeps a usable bearing throughout. It rounds the box on the blended heading without ever falling back on the map. In both cases it reaches a beacon the obstacle had hidden, which answers the third research question. \textcolor{red}{same too detail for conclusion. and you need to rewrite what is the bring away for each question? for example the last research question. the most important thing is only when there is an obstacle blocking the light how can we still mangae to detect the obstacle and readh the target? we show that original approach immediately fail and our's fusino approach and maintain efficiency while detecting obstacle, avoiding the drone from crashing in the clttering space.}

The contribution is not tied to the CrazyFlie. Huang et al.~\cite{huang2026lta} built the blimp and the simulator this work uses. In a collaboration with them, the same board and fused controller also fly on the real blimp, as Section~\ref{sec:blimp-generalisation} reports. Only the low-level motor control is adapted to its different airframe. On the blimp they reach several beacons and avoid obstacles just as they do on the quadrotor. This shows the navigation depends on the light sensing rather than on the specifics of the platform. \textcolor{red}{no need to talk about this in a whole paragraph. we already mention this at the end of previous section. just use 1 to 2 sentence is enough}

The three research questions are therefore answered in the affirmative \textcolor{red}{how many challenges is solve? with these solve, how many demonstration  we have shown? and what is the strong advance, or good stuff about our research is attribute to this community?}: the sensing is feasible within the drone's budget, the drone reaches several beacons in turn, and it routes around an obstacle that hides its beacon. The prior work this thesis extends could reach only a single beacon in open space. The board and fused controller developed here give a constrained micro-drone both the multi-beacon traversal and the obstacle avoidance it lacked, using only on-board light sensing. They do so across two different airframes.

\section{Limitations}
\label{sec:limitations}

Even though our system provide a promising novel sensing system for indoor autonomous drone operation, there is still some limitation with our current implementaion. The first limitation of the current implementation is its operating range, which is bounded by the photodiode sensing circuit. When the drone is far from a beacon, the modulated signal becomes weak relative to steady background light, causing the SNR to fall below the level needed for reliable navigation, as measured in Chapter~\ref{chp:realworld}. When the drone is very close to the beacon, the photodiodes can instead approach saturation, causing the recovered signal to flatten; the close-range dip observed in Section~\ref{sec:snr-field} suggests this upper bound. The usable region therefore lies between these two limits, where the beacon is neither too weak to distinguish from the background nor too strong for the sensor front end to measure linearly. This limitation comes from the current circuit implementation rather than from visible-light navigation itself. A more carefully designed sensing front end, such as one with improved dynamic range or higher-order band-pass filtering to suppress ambient light, could widen the usable range at both ends.

Second, the current system is limited to fixed-altitude navigation because both the sensing board shape and the controller are planar. The photodiodes are arranged in a horizontal ring, as described in the PCB design in Chapter~\ref{chp:hardware}, so the bearing estimate only resolves direction within that plane. Similarly, the algorithms described in Chapter~\ref{chp:algorithm} operate on a two-dimensional light map indexed by the drone’s horizontal position. Extending the method to full three-dimensional navigation is therefore limited more by hardware than by computation. Algorithmically, the map would become an $O(G^3)$ volume rather than an $O(G^2)$ grid for $G$ cells, and the local gradient fit would simply include a third coordinate. This increases computation, but not prohibitively. The larger challenge is sensing coverage. The present board places $N$ photodiodes around a single horizontal ring, with $N=8$ in Chapter~\ref{chp:hardware}. Covering a sphere with comparable angular spacing would require multiple rings over elevation, increasing the sensor count to roughly $O(N^2)$. Thus, the main bottleneck for three-dimensional navigation is the size, weight, and power cost of the photodiode array, rather than the gradient algorithm itself.

Third, real-world results are demonstrations rather than a statistical measure of reliability. We flew many more missions than the handful shown in Chapters~\ref{chp:multibeacon} and~\ref{chp:obstacle}, and the drone reached its beacon on most of them. But we did not run a controlled repeatability study. These flights therefore show that the multi-beacon traversal and the obstacle avoidance work, rather than how often they succeed. \textcolor{red}{i dont think this is necessary. but if you want mention still you need to talk about why success rate is important? why we should do this in the future}

Last, in our experiment, we assume the drone is flying in a static environment. In all experiments, the beacons and obstacles remain fixed while the drone navigates. The light map described in Chapter~\ref{chp:algorithm} is built under this assumption: each measurement is stored in a grid cell and then reused as if the underlying light field remains unchanged. If a beacon moves, or if an obstacle shifts after the drone has mapped its shadow, the map can contain stale values that no longer match the environment. The controller may then follow an outdated gradient. The present results therefore apply to environments that remain stable during navigation, while dynamic environments are left for future work.
