\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

Throughout my studies, I found myself increasingly drawn to the practical application of the theories we learned in class. This preference ultimately led me to choose the subject of this thesis. Beyond its practical aspects, the growing relevance of drones in today's geopolitical landscape further sparked my interest in the topic. The initial direction of this thesis also offered a considerable degree of freedom, for which I am grateful to my thesis advisor and supervisor. This freedom gave me the opportunity to design my own printed circuit board for the first time. Reaching that milestone made me feel that this thesis truly brought my studies full circle, truely coupling my computer science background with my studies in Computer and Embedded Systems Engineering.


\vspace{1\baselineskip}

I would first like to thank my daily supervisor, Harry Huang, not only for providing the foundation for this work, but also for his excellent guidance, support, and encouragement throughout the completion of this thesis. I would also like to thank my thesis advisor, Marco Zuñiga Zamalloa, for his guidance and the critical questions that helped shape this thesis into its final form. Finally, I would like to thank my roommates, family, colleagues, and girlfriend for patiently listening to my endless explanations and discussions about this work. Without you all serving as my rubber ducks, I would never have arrived at many of the insights that made this thesis possible.

\vspace{1\baselineskip}

\reportAuthor

\vspace{1\baselineskip}

\noindent
Delft, The Netherlands

\noindent
\today